### 2012-08-14 notes/coop.tex
Added
Changes

In \cite {ShohamLeytonBrown09} section 6.1 there is discussion of repeated games.

@@

>>>>

In \cite {ShohamLeytonBrown09} section 6.1 and chapter 8 of \cite{RePEc:mtp:titles:0262650401}, there is discussion of repeated games.

@@

\cite{Chalkiadakis_simplecoalitional} Theorem 3 provides an efficient algorithm for checking wether the core is non-empty or wether a given demand vector is in the core. Indeed, we can first check, for each player $i \in N$, if $i$ is a veto player (by Theorem 2, this can be done in polynomial time). The core is non-empty if the answer is "`yes"' for at least one $i \in N$. Furthermore, to check if d is in the core, we can check if $d_i > 0$ for any non-veto player $i$; if answer is "`yes"', d is not in the core.
